### 2020-05-30 README.Rmd
readme

The goal of neonstore is to ...

@@

You can install the released version of neonstore from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("neonstore")
```

And the development version from [GitHub](https://github.com/) with:

@@

```{r example}
library(neonstore)
neon_download("DP1.10003.001", file_regex = "[.]csv")

@@

Now, view your library of NEON products:

```{r }
meta <- neon_index()
```

>>>>

The goal of neonstore is to provide access and persistent storage of NEON data tables

@@

Install the development version from [GitHub](https://github.com/) with:

@@

```{r example, cache=TRUE}
library(neonstore)
neon_download("DP1.10003.001", file_regex = "[.]csv")

@@

Now, view your library of NEON products.  These will persist between sessions, 
so you only need to download once, or to retrieve updates.

```{r }
neon_tables()
```
See files associated with a given table,

```{r output="hide"}
meta <- neon_index("brd_countdata") 
meta
```

```{r echo=FALSE}
# pretty-print
tibble::as_tibble(meta)
```

Read in all the component tables into a single data.frame

```{r}
brd_countdata <- neon_read(meta)
```
